\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-11-23 paper.tex
improved future work on relation to FRP

As a next step, we want to investigate the relation of \NAME's DSL to reactive
programming. Both clearly share common concepts with respect to
event-drivenness and the absence of e.g. explicit loops.

>>>>

As a next step, we want to investigate the relation of \NAME to other
programming paradigms such as functional reactive programming. They share
common concepts with respect to event-drivenness and the preference to avoid
explicit loops.
